Proportional multi-state multiple-cohort life table model

### 2018-05-02 MSLT/MSLTdoc.Rmd
Move legend function to function scr
ipt

23) Plot outcomes for each age and sex cohort using created function. ADD A LOOP TO GENERATE ALL OUTCOMES FOR IN_AGE, IN_POPULATION, IN_OUTCOMES AND IN_LEGEND. FIX THE COLORS IN THE FUNCTION.

@@

require(ggplot2)
require(gridExtra)
require(grid)

grid_arrange_shared_legend <- function(..., ncol = length(list(...)), nrow = 1, position = c("bottom", "right"), mainTitle = "", mainLeft = "", mainBottom = "") {

  plots <- list(...)
  position <- match.arg(position)
  g <- ggplotGrob(plots[[1]] + theme(legend.position = position))$grobs
  legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
  lheight <- sum(legend$height)
  lwidth <- sum(legend$width)
  gl <- lapply(plots, function(x) x + theme(legend.position="none"))
  gl <- c(gl, ncol = ncol, nrow = nrow, top = mainTitle, left = mainLeft, bottom = mainBottom)

  combined <- switch(position,
                     "bottom" = arrangeGrob(do.call(arrangeGrob, gl),
                                            legend,
                                            ncol = 1,
                                            heights = unit.c(unit(1, "npc") - lheight, lheight)),
                     "right" = arrangeGrob(do.call(arrangeGrob, gl),
                                           legend,
                                           ncol = 2,
                                           widths = unit.c(unit(1, "npc") - lwidth, lwidth)))

  #grid.newpage()
  grid.draw(combined)

  # return gtable invisibly
  invisible(combined)

g_legend <- function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)
}

@@

@@

                pdf(paste0(output_dir, "/", paste(age, sex, outcome, sep="_"), ".pdf"))
                grid_arrange_shared_legend (p1, p2, p3, p4, ncol = 2, nrow = 2, mainTitle = paste(age, sex, outcome),
                                          mainLeft = 'Cases', mainBottom = 'Age')
                dev.off()

@@

@@

## Use plot_grid in a loo/grid.arrange

# mpage_male <- do.call(marrangeGrob, list(grobs=p_list_male, nrow = 2, ncol = 2))
# mpage_male
# 
# 
# lay <- rbind(c(1, 2),
#              c(3, 4),
#              c(5, NA))
# 
# 
# mpage_female <- do.call(marrangeGrob, list(grobs=p_list_female, layout_matrix = lay))
# mpage_female

## Trying to use ggarrange
# mpage2 <- ggarrange(plotlist = p_list, ncol = 3, nrow = 3)

# ggsave("graphs/multipage.jpeg", mpage)

#Check ggarrange in ggpubr

#http://www.sthda.com/english/wiki/print.php?id=177
```

>>>>

23) Plot outcomes for each age and sex cohort using created functions. Two functions are used: plot_output (plots outputs) and grid_arrange_shared_legend (places one label per page).

@@

@@

            # There are 4 diseases for males, this should be modified according to the modelled 
            # diseases.

@@

                pdf(paste0(output_dir, "/", paste(age, sex, outcome, sep="_"), ".pdf"))
                grid_arrange_shared_legend (p1, p2, p3, p4, ncol = 2, nrow = 2, mainTitle = paste(age, sex, outcome),mainLeft = 'Cases', mainBottom = 'Age')
                dev.off()

@@

            # There are 5 diseases for females, this should be modified according to the modelled 
            # diseases.

@@
